On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Work a bit more on FBQP

Define the language $L_{f, i, b}$ s.t. $x\in L_{f, i, b}$ if the $i$th bit of $f(x)$ is $b$.

@@

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how}
	Let $\cL = \set{L_{f, i, b}: i\in[m], b\in\set{0, 1}}$
	\begin{enumerate}
		\item Run \cref{proto:repQPIP0BQP} for all languages $L\in\cL$ in parallel
		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{f, i, 1}$ gives the same output, reject.
		\item Otherwise, define $y_i = b$ where $x\in L_{f, i, b}$. This gives $y\in\set{0,1}^m$
		\item Verifier outputs $y$
	\end{enumerate}
\end{protocol}

\begin{theorem}
	\cref{QPIP0FBQP} has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	TODO
\end{prf}

>>>>

For any input $x\in\set{0, 1}^*$, define $f_i(x)$ to be the $i$-th bit of $f(x)$.

Define the language $L_{i, b}=\set{x:f_i(x)=b}$.

@@

	Suppose without loss of generality that the verifier knows $f(x)$ is of length $m=\poly(n)$ \Ethan{Seems like a strong assumption; maybe need to explain how}
	Let $\cL = \set{L_{i, b}: i\in[m], b\in\set{0, 1}}$
	\begin{enumerate}
		\item Run \cref{proto:repQPIP0BQP} for all languages $L\in\cL$ in parallel
		\item If $\exists i$ s.t. $x\in L_{f, i, 0}$ and $x\in L_{i, 1}$ gives the same output, reject.
		\item Otherwise, define $y_i = b$ where $x\in L_{i, b}$. This gives $y\in\set{0,1}^m$
		\item Verifier outputs $y$
	\end{enumerate}
\end{protocol}

\begin{theorem}
	\cref{QPIP0FBQP} has negligible completeness and soundness, and is blind.
\end{theorem}
\begin{prf}
	Completeness is follows by inspection.
	Blindness follows because the executions of \cref{proto:repQPIP0BQP} are blind.

	Soundness... TODO
\end{prf}
